\newcommand{\CLASSINPUTtoptextmargin}{0.75in}
\newcommand{\CLASSINPUTbottomtextmargin}{0.75in}
\newcommand{\CLASSINPUTinnersidemargin}{0.75in}
\newcommand{\CLASSINPUToutersidemargin}{0.75in}
\documentclass[letterpaper,conference,10pt]{ieeetran}
\IEEEoverridecommandlockouts
\overrideIEEEmargins
\pdfoptionpdfminorversion=4
%\usepackage[sc]{mathpazo}
%\linespread{1.02}         % Palatino needs more leading (space between lines)
\usepackage[T1]{fontenc}


\usepackage{multicol}
% Insert hyperlinks in the document
\usepackage{hyperref}
\hypersetup{bookmarksopen,bookmarksnumbered,
pdfpagemode=UseOutlines,
colorlinks=true,
linkcolor=blue,
anchorcolor=blue,
citecolor=blue,
filecolor=blue,
menucolor=blue,
urlcolor=blue
}
\usepackage{amsmath, amssymb, amsfonts, amsthm}
\usepackage{bm}
%\usepackage{subcaption}
\usepackage{flushend}
\usepackage{dirtree}
\usepackage{graphicx}
\usepackage{mathtools}
\usepackage[numbers,sort&compress]{natbib}
\usepackage{fixltx2e}

% Labels in IEEE format
\newcommand{\eref}[1]{(\ref{#1})} % Equation
\newcommand{\sref}[1]{Sec. \ref{#1}} % Section
\newcommand{\figref}[1]{Fig.\ref{#1}} % Figure
\newcommand{\tref}[1]{Table \ref{#1}} % Table



% floats
\usepackage[font=footnotesize]{caption} % incompatible with aaai.sty?
%\usepackage[font=footnotesize]{subcaption}
\usepackage{mathabx}
\usepackage{verbatim}
\usepackage{algorithm}
\usepackage{amsmath}
\usepackage[noend]{algpseudocode}


\usepackage{multirow}
\usepackage{booktabs}
\usepackage[dvipsnames]{xcolor}

\setlength{\textfloatsep}{5pt}
\setlength{\intextsep}{5pt}

\newcommand{\ssnote}[1]{{\xxnote{SS}{red}{#1}}}
\newcommand{\scnote}[1]{{\xxnote{SC}{blue}{#1}}}
\newcommand{\cdnote}[1]{{\xxnote{CD}{cyan}{#1}}}
\newcommand{\xxnote}[3]{}
\ifx\hidenotes\undefined
 \usepackage{color}
 \renewcommand{\xxnote}[3]{\color{#2}{#1: #3}}
\fi

\ifCLASSOPTIONcompsoc
  \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
\else
  \usepackage[caption=false,font=footnotesize]{subfig}
\fi

\DeclareMathOperator*{\argmin}{\arg\!\min}

\begin{document}

\title{\vspace{0.20in}\LARGE A Sensor Fusion Approach For }

\author{Pengju Jin, Pyry Matikainen, Siddhartha Srinivasa}
\maketitle 	

\begin{abstract}
Although there is an abundance of planar fiducial-marker systems proposed for augmented reality and computer-vision purposes, none of them are robust enough to estimate the pose accurately in robotic applications where tags are small and the collected data are noisy. This is inherently a difficult problem because these fiducial marker systems work solely within the RGB image space and the resolution of cameras on robots is constrained. As a result, small noise in the image would cause the tag's detection process to produce large pose estimation errors. 

This paper describes an algorithm that improves the pose estimation accuracy of square fiducial markers in difficult scenes by fusing information from RGB and depth sensors. The algorithm retains the high detection rate and low false  positive rate characteristics of fiducial systems while making them much more robust to size, lighting and sensory noise for pose estimation. The improvements make the fiducial tags suitable for robotic tasks requiring high pose accuracy in the real world environment.
\end{abstract}

\IEEEpeerreviewmaketitle

\input{sections/introduction}

\input{sections/related}

\input{sections/problem}

\input{sections/approach}

\input{sections/results}

\input{sections/conclusion}

{\footnotesize
\bibliographystyle{ieeetr}
\bibliography{bib/references}}

\end{document}

